A Sample Thesis

### 2014-04-14 thesis-template/mitsample.tex
thunk

%% LyX 1.6.7 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english,msc]{ubcthesis}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{longtable}
\usepackage{url}
\usepackage{graphicx}
\usepackage{esint}
\usepackage[numbers]{natbib}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
%%
%% This is file `ubcsample.tex',
%% generated with the docstrip utility.
%
% The original source files were:
%
% ubcthesis.dtx  (with options: `ubcsampletex')
%% 
%% This file was generated from the ubcthesis package.
%% --------------------------------------------------------------
%% 
%% Copyright (C) 2001
%% Michael McNeil Forbes
%% mforbes@alum.mit.edu
%% 
%% This file may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.2
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% This program is distributed in the hope that it will be useful,
%% but WITHOUT ANY WARRANTY; without even the implied warranty of
%% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
%% LaTeX Project Public License for more details.
%% 
%% This program consists of the files ubcthesis.dtx, ubcthesis.ins, and
%% the sample figures fig.eps and fig.fig.
%% 
%% This file may be modified and used as a base for your thesis without
%% including the licence agreement as long as the content (i.e. textual
%% body) of the file is completely rewritten. You must, however, change
%% the name of the file.
%% 
%% This file may only be distributed together with a copy of this
%% program. You may, however, distribute this program without generated
%% files such as this one.
%%

% This Sample thesis requires \LaTeX2e
\NeedsTeXFormat{LaTeX2e}[1995/12/01]
\ProvidesFile{ubcsample.tex}[2010/06/13 v1.66 ^^J
 University of British Columbia Sample Thesis]
% This is the \documentclass[]{} command.  The manditory argument
% specifies the "flavour" of thesis (ubcthesis for UBC).  The
% optional arguments (in []) specify options that affect how the
% thesis is displayed.  Please see the ubcthesis documentation for
% details about the options.

%
% To compile this sample thesis, issue the following commands:
% latex ubcsample
% bibtex ubcsample
% latex ubcsample
% latex ubcsample
% latex ubcsample
%
% To view use xdvi (on unix systems):
% xdvi ubcsample.dvi
%
% To make a postscript file, use dvips:
% dvips -o ubcsample.ps ubcsample.dvi
%
% To view the postscript file, use ghostview or gv (on unix systems):
% gv ubcsample.ps
%
%************************************************
% Optional packages.
%
% The use of these packages is optional, but they provide various
% tools for more flexible formating.  The sample thesis uses these,
% but if you remove the example code, you should be able to exclude
% these packages.  Only standard packages have been described here;
% they should be installed with any complete LaTeX instalation, but
% if not, you can find them at the Comprehensive TeX Archive Network
% (CTAN): http://www.ctan.org/
%

@@

%******** float *********************************
% This package allows you to customize the style of
% "floats"---floating objects such as figures and tables.  In
% addition, it allows you to define additional floating objects which
% may be included in a list similar to that produces by \listoftables
% and \listoffigures.  Common uses include introducing floats for
% programs and other code bits in Compute Science and Chemical Schema.
\usepackage{float}

%******** tocloft *******************************
% This package allows you to customize and define custom lists such
% as a list of programs or Chemical Scheme.  Note: if you use the
% subfigure package, you must specify that you do as an option here.
% The title option uses the default formatting.  We do not use this
% here as the default formatting is acceptable.  Use the float
% package instead unless you need the extra formatting control
% provided by tocloft.
%\usepackage[subfigure, titles]{tocloft}

%******** alltt *********************************
% The alltt package allows you to include files and have them
% formatted in a verbatim fashion.  This is useful for including
% source code from an additional file.
%\usepackage{alltt}

%******** listings ******************************
% The listings package may be used to include chunks of source code
% and has facilities for pretty-printing many languages.
%\usepackage{listings}

%******** longtable *****************************
% The longtable package allows you to define tables that span
% multiple pages.
\usepackage{longtable}

%******** graphics and graphicx *****************
% This allows you to include encapsulated postscript files.  If you
% don't have this, comment the \includegraphics{} line following the
% comment "%includegraphics" later in this file.

%******** subfigure *****************************
% The subfigure package allows you to include multiple figures and
% captions within a single figure environment.
%\usepackage{subfigure}

%******** here **********************************
% The here package gives you more control over the placement of
% figures and tables.  In particular, you can specify the placement
% "H" which means "Put the figure here" rather than [h] which means
% "I would suggest that you put the figure here if you think it looks
% good."
%\usepackage{here}

%******** natbib ********************************
% This is a very nice package for bibliographies.  It includes options
% for sorting and compressing bibliographic entries.

@@

%******** setspace *******************************
% The setspace package allows you to manually set the spacing of the
% file.  UBC may require 1.5 spacing for microfilming of theses.  In
% this case you may obtain this by including this package and issuing
% one of the following commands:
%\usepackage{setspace}
%\singlespacing
%\onehalfspacing
%\doublespacing

% These commands are optional.  The defaults are shown.  You only
% need to include them if you need a different value
\institution{The University Of British Columbia}

% If you are at the Okanagan campus, then you should specify these
% instead.
%\faculty{The College of Graduate Studies}
%\institutionaddress{Okanagan}
\faculty{The Faculty of Graduate Studies}
\institutionaddress{Vancouver}

% You can issue as many of these as you have...
\previousdegree{B.Sc., The University of British Columbia, 1999}
\previousdegree{M.Sc., The University of British Columbia, 2001}
\previousdegree{Ph.D., Massachusetts Institute of Technology, 2005}

@@

% These commands are required.
\title{A Sample UBC Thesis}
\subtitle{With a Subtitle}
\author{Michael M$^{\rm c}$Neil Forbes}
\copyrightyear{2000}
\submitdate{\today} % The "\ " is required after
                                      % \monthname to prevent the
                                      % command from eating the space.
\program{Physics}

% These commands are presently not required for UBC theses as the
% advisor's name and title are not presently required anywhere.
%\advisor{Ariel R.~Zhitnitsky}
%\advisortitle{Professor of Physics}

% One might want to override the format of the section and chapter
% numbers.  This shows you how to do it.  Note that the current
% format is acceptable for submission to the FoGS: If you wish to modify
% these, you should check with the FoGS explicity. prior to making
% the modifications.
\renewcommand{\thepart}{\Roman{part}}
\renewcommand{\thechapter}{\arabic{chapter}}
\renewcommand{\thesection}{\thechapter.\arabic{section}}
\renewcommand{\thesubsection}{\thesection.\arabic{subsection}}
\renewcommand{\thesubsubsection}{\thesubsection.\arabic{subsubsection}}
\renewcommand{\theparagraph}{\thesubsubsection.\arabic{paragraph}}
\renewcommand{\thesubparagraph}{\theparagraph.\arabic{subparagraph}}

% Here is an example of a "Program" environment defined with the
% "float" package.  The list of programs will be stored in the file
% ubcsample.lop and the numbering will start with the chapter
% number.  The style will be "ruled".
\floatstyle{ruled}
\newfloat{Program}{htbp}{lop}[chapter]

% Here is the start of the document.

\makeatother

\usepackage{babel}

\begin{document}
% This starts numbering in Roman numerals as required for the thesis
% style.
\frontmatter % Mandatory

% The order of the following components should be preserved.  The order
% listed here is the order currently required by FoGS.
% Mandatory
% Mandatory -  maximum 350 words

\begin{abstract}
The \texttt{genthesis.cls} \LaTeX{} class file and accompanying documents,
such as this sample thesis, are distributed in the hope that it will
be useful but without any warranty (without even the implied warranty
of fitness for a particular purpose). For a description of this file's
purpose, and instructions on its use, see below.

@@

Michael Forbes. mforbes@physics.ubc.ca 
\end{abstract}
\tableofcontents{}% Mandatory
\listoftables
% Mandatory if thesis has tables
\listoffigures
% Mandatory if thesis has figures
\listof{Program}{List of Programs} % Optional
% Any other lists should come here, i.e.
% Abbreviation schemes, definitions, lists of formulae, list of
% schemes, glossary, list of symbols etc.

\chapter{Acknowledgements}

% Optional
This is the place to thank professional colleagues and people who
have given you the most help during the course of your graduate work.

\chapter{Dedication}

% Optional
The dedication is usually quite short, and is a personal rather than
an academic recognition. The \emph{Dedication} does not have to be
titled, but it must appear in the table of contents. If you want to
skip the chapter title but still enter it into the Table of Contents,
use this command \verb|\chapter[Dedication]{}|.

\chapter{Statement of Co-Authorship}

% Manditory if thesis co-written
If any part of your thesis was co-written, you must include a Co-Authorship
statement which gives details of your contribution to the following
areas:
\begin{itemize}
\item identification and design of research program 
\item performing the research 
\item data analyses 
\item manuscript preparation 
\end{itemize}
Note that this section is the last of the preliminary pages (with
lowercase Roman numeral page numbers). It must be placed \emph{before}
the \verb|\mainmatter| command. After that, Arabic numbered pages
will begin.

% Any other unusual prefactory material should come here before the
% main body.

% Now regular page numbering begins.
\mainmatter

% Parts are the largest structural units, but are optional.
%\part{Thesis}

% Chapters are the next main unit.

\chapter{This is a Chapter}

% Sections are a sub-unit

\section{A Section}

Here is a section with some text. Equations look like this $y=x$.%
\footnote{Here is a footnote.%
}

@@

% Subsections follow

\subsection{This is a Subsection}

Here is an example of a citation: \citep{Forbes:2006ba}. The actual
form of the citation is governed by the bibliographystyle. These citations
are maintained in a BIB\TeX{} file \texttt{sample.bib}. You could
type these directly into the file. For an example of the format to
use look at the file \texttt{ubcsample.bbl} after you compile this
file.%
\footnote{Here is another footnote.%
}

@@

\subsubsection{This is a Subsubsection}

Here are some more citations \citep{LL3:1977,Peccei:1989,Turner:1999}.
If you use the \texttt{natbib} package with the \verb+sort&compress+
option, then the following citation will look the same as the first
citation in this section: \citep{Turner:1999,Peccei:1989,LL3:1977}.

@@

\paragraph{This is a Paragraph}

Paragraphs and subparagraphs are the smallest units of text. There
is no subsubsubsection etc.

\subparagraph{This is a Subparagraph}

This is the last level of organisation. If you need more than this,
you should consider reorganizing your work\dots

\begin{equation}
\mathrm{f}(x)=\int_{-\infty}^{\int_{-\infty}^{x}e^{-\frac{y^{2}}{2}}\mathrm{d}{y}}e^{-z^{2}}\mathrm{d}z\end{equation}

In order to show you what a separate page would look like (i.e. without
a chapter heading) I must type some more text. Thus I will babble
a bit and keep babbling for at least one more page\ldots{} What you
should notice is that the chapter titles appear substantially lower
than the continuing text. Babble babble babble babble babble babble
babble babble babble babble babble babble babble babble babble babble
babble babble babble babble babble babble babble babble babble babble
babble babble babble babble babble babble babble babble babble babble
babble babble babble babble babble.

@@

%
\begin{table}[t]
 %optional [t, b or h];
 \begin{tabular}{|r||r@{.}l}
\hline 
Phoenix  & \$960 & 35\tabularnewline
\hline 
Calgary  & \$250 & 00\tabularnewline
\hline
\end{tabular}\caption[Here is the caption for this wonderful table\ldots{}]{ \label{tab:Table1} Here is the caption for this wonderful table.
It has not been centered and the positioning has been specified to
be at the top of the page. Thus it appears above the babble rather
than below where it is defined in the source file.}

\end{table}

% Force a new page: without this, the quote would appear on the
% previous page.
\newpage{}

\section{Quote}

% It is centered

\begin{quote}
\begin{center}
This is a small poem,\\
 a little poem, a Haiku,\\
 to show you how to.\\
 ---Michael M$^{{\rm c}}$Neil Forbes. 
\par\end{center}
\end{quote}
This small poem shows several features: 
\begin{itemize}
\item The use of the \verb|quote| and \verb|center| environments. 
\item The \verb|\newpage| command has been used to force a page break.
(Sections do not usually start on a new page.) 
\item The pagestyle has been set to suppress the headers using the command
\verb|\thispagestyle{plain}|. Note that using \verb|\pagestyle{plain}|
would have affected all of the subsequent pages. 
\end{itemize}

\section{Programs}

Here we give an example of a new float as defined using the \texttt{float}
package. In the preamble we have use the commands \begin{verbatim}
\floatstyle{ruled} \newfloat{Program}{htbp}{lop}{[}chapter{]}
\end{verbatim} This creates a {}``Program'' environment that may
be use for program fragments. A sample \texttt{python} program is
show as Program~\ref{prog:fib}. (Note that Python places a fairly
restrictive limit on recursion so trying to call this with a large
$n$ before building up the cache is likely to fail unless you increase
the recursion depth.) \begin{Program} \caption{\label{prog:fib} Python program that computes the $n^{{\rm th}}$
Fibonacci number using memoization.}

\begin{verbatim} def fib(n,cache={}): if n < 2: return 1 if n in
cache: return cache{[}n{]} else: result = fib(n-1)+fib(n-2) cache{[}n{]}
= result return result \end{verbatim} \end{Program} Instead of using
a \texttt{verbatim} environment for your program chunks, you might
like to \texttt{include} them within an \texttt{alltt} envrironment
by including the \verb|\usepackage{alltt}| package (see page 187
of the \LaTeX{} book). Another useful package is the \verb|\usepackage{listings}|
which can pretty-print many different types of source code.

% Force a new page
\newpage{}

% Here we provide a short optional argument to \chapter[]{}.  This
% optional argument will appear in the table of contents.  For long
% titles, one should use this to give a single-line entry to the
% table of contents.

\chapter[Another Chapter\ldots{}]{Another Chapter with a Very Long Chapter-name that will Probably
Cause Problems}

This chapter name is very long and does not display properly in the
running headers or in the table of contents. To deal with this, we
provide a shorter version of the title as the optional argument to
the \verb|\chapter[]{}| command.

For example, this chapter's title and associated table of contents
heading and running header was created with\\
 \verb|\chapter[Another Chapter\ldots]{Another Chapter with a Very Long|\\
 \verb|Chapter-name that will Probably Cause Problems}|.

Note that, according to the thesis regulations, the heading included
in the table of contents must be a truncation of the actual heading.

\section{Another Section}

Another bunch of text to demonstrate what this file does. You might
want a list for example:%
\footnote{Here is a footnote in a different chapter. Footnotes should come after
punctuation.%
} 
\begin{itemize}
\item An item in a list. 
\item Another item in a list. 
\end{itemize}

\section*{An Unnumbered Section That is Not Included in the Table of Contents}

Here is an example of a figure environment. %
\begin{figure}[ht]
 %psfrag: comment the following line if not using the psfrag package

\centering{}\psfrag{pie makes me happy!}{$\pi$ makes me happy!}
%includegraphics: comment the following if not using the graphicx package
 \includegraphics[width=0.4\textwidth]{fig} \caption[Happy Face: figure example.]{\label{fig:happy} This is a figure of a happy face with a \texttt{psfrag}
replacement. The original figure (drawn in xfig and exported to a
.eps file) has the text {}``pie makes me happy!''. The \texttt{psfrag}
package replaces this with {}``$\pi$ makes me happy!''. Note that
we have used the optional argument for the caption command so that
only a short version of this caption occurs in the list of figures.}

\end{figure}

\afterpage{\clearpage{}} Perhaps I should say that the example
of a figure can be seen in Figure~\ref{fig:happy}. Figure placement
can be tricky with \LaTeX{}\ because figures and tables are treated
as {}``floats'': text can flow around them, but if there is not
enough space, they will appear later. To prevent figures from going
too far, the \verb|\afterpage{\clearpage}| command can be used. This
makes sure that the figure appears on the following page.

@@

Figures can make a document more enjoyable as demonstrated by Figure~\ref{fig:happy}.

\section{Tables}

We have already included one table:~\ref{tab:Table1}. Another table
is plopped right here. %
\begin{table}[ht]

\centering{}\begin{tabular}{|l||l|l||l|l|}
\hline 
 & \multicolumn{2}{l|}{Singular} & \multicolumn{2}{l|}{Plural}\tabularnewline
\hline 
 & English & \textbf{Gaeilge} & English & \textbf{Gaeilge}\tabularnewline
\hline
\hline 
1st Person & at me & \textbf{agam} & at us & \textbf{againn}\tabularnewline
2nd Person & at you & \textbf{agat} & at you & \textbf{agaibh}\tabularnewline
3rd Person & at him & \textbf{aige} & at them & \textbf{acu}\tabularnewline
 & at her & \textbf{aici} &  & \tabularnewline
\hline
\end{tabular}\caption{ \label{tab:Table2} Another table.}

\end{table}

Well, actually, as with Figure~\ref{fig:happy}, the table does not
necessarily appear right {}``here'' because tables are also {}``floats''.
\LaTeX{} puts them where it can. Becuase of this, one should refer
to floats by their labels rather than by their location. This example
is demonstrated by Table~\ref{tab:Table2}. This one is pretty close,
however.

Another useful package is \verb|\usepackage{longtable}| which provides
the \texttt{longtable} environment. This is nice because it allows
tables to span multiple pages. Table~\ref{tab:longtable} has been
formatted this way.

\begin{center}
\begin{longtable}{|l|l|l|}
\caption{\label{tab:longtable}Feasible triples for highly variable Grid}
\tabularnewline
\caption{\label{tab:longtable}Feasible triples for highly variable Grid}
\tabularnewline
\hline 
\multicolumn{1}{|c|}{\textbf{Time (s)}} & \multicolumn{1}{c|}{\textbf{Triple chosen}} & \multicolumn{1}{c|}{\textbf{Other feasible triples}}\tabularnewline
\endfirsthead
\hline 
\multicolumn{3}{c}{}\tabularnewline
\hline 
\multicolumn{1}{|c|}{\textbf{Time (s)}} & \multicolumn{1}{c|}{\textbf{Triple chosen}} & \multicolumn{1}{c|}{\textbf{Other feasible triples}}\tabularnewline
\hline
\endhead
\hline 
\multicolumn{3}{|r|}{{Continued on next page}}\tabularnewline
\hline
\endfoot
\hline 
0  & (1, 11, 13725)  & (1, 12, 10980), (1, 13, 8235), (2, 2, 0), (3, 1, 0) \tabularnewline
274  & (1, 12, 10980)  & (1, 13, 8235), (2, 2, 0), (2, 3, 0), (3, 1, 0) \tabularnewline
5490  & (1, 12, 13725)  & (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
8235  & (1, 12, 16470)  & (1, 13, 13725), (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
10980  & (1, 12, 16470)  & (1, 13, 13725), (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
13725  & (1, 12, 16470)  & (1, 13, 13725), (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
16470  & (1, 13, 16470)  & (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
19215  & (1, 12, 16470)  & (1, 13, 13725), (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
21960  & (1, 12, 16470)  & (1, 13, 13725), (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
24705  & (1, 12, 16470)  & (1, 13, 13725), (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
27450  & (1, 12, 16470)  & (1, 13, 13725), (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
30195  & (2, 2, 2745)  & (2, 3, 0), (3, 1, 0) \tabularnewline
32940  & (1, 13, 16470)  & (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
35685  & (1, 13, 13725)  & (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
38430  & (1, 13, 10980)  & (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
41175  & (1, 12, 13725)  & (1, 13, 10980), (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
43920  & (1, 13, 10980)  & (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
46665  & (2, 2, 2745)  & (2, 3, 0), (3, 1, 0) \tabularnewline
49410  & (2, 2, 2745)  & (2, 3, 0), (3, 1, 0) \tabularnewline
52155  & (1, 12, 16470)  & (1, 13, 13725), (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
54900  & (1, 13, 13725)  & (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
57645  & (1, 13, 13725)  & (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
60390  & (1, 12, 13725)  & (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
63135  & (1, 13, 16470)  & (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
65880  & (1, 13, 16470)  & (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
68625  & (2, 2, 2745)  & (2, 3, 0), (3, 1, 0) \tabularnewline
71370  & (1, 13, 13725)  & (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
74115  & (1, 12, 13725)  & (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
76860  & (1, 13, 13725)  & (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
79605  & (1, 13, 13725)  & (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
82350  & (1, 12, 13725)  & (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
85095  & (1, 12, 13725)  & (1, 13, 10980), (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
87840  & (1, 13, 16470)  & (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline
90585  & (1, 13, 16470)  & (2, 2, 2745), (2, 3, 0), (3, 1, 0) \tabularnewline

>>>>

%%
%% This is file `mitsample.tex',
%% generated with the docstrip utility.
%
% The original source files were:
%
% ubcthesis.dtx  (with options: `mitsampletex')
%% 
%% This file was generated from the ubcthesis package.
%% --------------------------------------------------------------
%% 
%% Copyright (C) 2001
%% Michael McNeil Forbes
%% mforbes@alum.mit.edu
%% 
%% This file may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.2
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% This program is distributed in the hope that it will be useful,
%% but WITHOUT ANY WARRANTY; without even the implied warranty of
%% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
%% LaTeX Project Public License for more details.
%% 
%% This program consists of the files ubcthesis.dtx, ubcthesis.ins, and
%% the sample figures fig.eps and fig.fig.
%% 
%% This file may be modified and used as a base for your thesis without
%% including the licence agreement as long as the content (i.e. textual
%% body) of the file is completely rewritten. You must, however, change
%% the name of the file.
%% 
%% This file may only be distributed together with a copy of this
%% program. You may, however, distribute this program without generated
%% files such as this one.
%%

% This Sample thesis requires \LaTeX2e
\NeedsTeXFormat{LaTeX2e}[1995/12/01]
\ProvidesFile{mitsample.tex}[2012/04/07 v1.70 ^^J
 Massachusetts Institute of Technology Sample Thesis]

\documentclass[msc,10pt,oneside]{mitthesis}
%
% To compile issue the following commands:
% latex mitsample
% bibtex mitsample
% latex mitsample
% latex mitsample
% latex mitsample
%
% To view use xdvi (on unix systems):
% xdvi mitsample.dvi
%
% To make a postscript file, use dvips:
% dvips -o mitsample.ps mitsample.dvi
%
% To view the postscript file, use ghostview or gv (on unix systems):
% gv mitsample.ps
%
%************************************************
% Optional packages.
%
% The use of these packages is optional: they are standard now and
% should be installed on your system, but if they are not, you might
% have to comment out the appropriate lines to get this file to
% compile.
%
%******** natbib ********************************
% This is a very nice package for bibliographies.  It includes options
% for sorting and compressing bibliographic entries.
\usepackage[numbers,sort&compress]{natbib}

%******** graphics and graphicx ******************************
% This allows you to include encapsulated postscript files.  If you
% don't have this, comment the \includegraphics{} line following the
% comment "%includegraphics" later in this file.
\usepackage{graphicx}

@@

@@

% These commands are optional.  The defaults are shown.
\institution{Massachusetts Institute of Technology}
\institutionaddress{Cambridge}
\program{Physics}

% You can issue as many of these as you have...
\previousdegree{B.Sc., The University of British Columbia, 1999}
\previousdegree{M.Sc., The University of British Columbia, 2001}

@@

% These commands are required.
\title{A Sample Thesis}
\subtitle{With a Subtitle}
\author{Michael M$^{\rm c}$Neil Forbes}
\copyrightyear{2000}
\submitdate{June 2004}

% These commands are required by MIT.
\advisor{Frank Wilczek}
\advisortitle{Herman Feshbach Professor of Physics}
\chairman{Thomas Greytak}{Professor and Associate Department Head for
  Education}
% One might want to override the format of the section and chapter
% numbers.  This shows you how to do it.  Note that
\renewcommand\thepart         {\Roman{part}}
\renewcommand\thechapter      {\arabic{chapter}}
\renewcommand\thesection      {\thechapter.\arabic{section}}
\renewcommand\thesubsection   {\thesection.\arabic{subsection}}
\renewcommand\thesubsubsection{\thesubsection.\arabic{subsubsection}}
\renewcommand\theparagraph    {\thesubsubsection.\arabic{paragraph}}
\renewcommand\thesubparagraph {\theparagraph.\arabic{subparagraph}}

\setcounter{tocdepth}{2}
\setcounter{secnumdepth}{2}

% Here is the start of the document.
\begin{document}

% Unlike the UBC thesis, page numbering for MIT theses should start
% at 1 and continue.  Thus, there is no \frontmatter command issued
% here as there was for the UBC thesis.

\maketitle
\authorizationform
\begin{abstract}
  The \texttt{genthesis.cls} \LaTeX{} class file and accompanying
  documents, such as this sample thesis, are distributed in the hope
  that it will be useful but without any warranty (without even the
  implied warranty of fitness for a particular purpose).  For a
  description of this file's purpose, and instructions on its use, see
  below.

@@

  Michael Forbes.
  mforbes@alum.mit.edu
\end{abstract}

\tableofcontents
\listoftables
\listoffigures
% Any other lists should come here, i.e.
% Abbreviation schemes, definitions, lists of formulae, list of
% schemes, etc.

\chapter{Preface}
These papers have been published earlier\ldots.

\chapter{Acknowledgements}
Thank you mother here.

% Force a new page.
\newpage

% Any other unusual sections should come here between the
% acknowledgements and the main body.

% Suppress the running headers for this page only.
\thispagestyle{plain}
\chapter*{Disclaimer} % Unnumbered
The \texttt{mitthesis} \LaTeX{} class and the accompanying sample files
are \emph{unofficial} and are not supported by the Massachusetts
Institute of Technology.  While I have attempted to make the style
file and sample files conform to all of the requirements set forth by
the library, you should always consult one of the library staff
members for assistance with problems \emph{before} starting final
draft.  You should be able to find the thesis requirements at one of
the following sites:
\begin{table}[h]
  \begin{center}
    \begin{tabular}{|l|}
      \hline
      \url{http://libraries.mit.edu/archives/thesis-specs/}\\
      \url{http://libraries.mit.edu/archives/index.html}\\
      \hline
    \end{tabular}
  \end{center}
  \caption{\label{tab:ubcurls}
    Potential sources of information regarding thesis preparation at MIT.}
\end{table}

% Force a new page.
\newpage

% Suppress the running headers for this page only.
\thispagestyle{plain}

% Here we provide a short optional argument to \chapter[]{}.  This
% optional argument will appear in the table of contents.  For long
% titles, one should use this to give a single-line entry to the
% table of contents.
\chapter[Poem]{A Japanese Introduction}

% Here is a quote:
\begin{quote}
  % It is centered
  \begin{center}
    This is a small poem,\\
    a little poem, a Haiku,\\
    to show you how to.\\
    ---Michael Forbes.
  \end{center}
\end{quote}
This small poem shows several features:
\begin{itemize}
\item The \verb|\newpage| command has been used to force a page break.
\item The pagestyle has been set to suppress the headers using the
  command \verb|\thispagestyle{plain}|.  Note that using
  \verb|\pagestyle{plain}| would have affected all of the subsequent
  pages.
\item The \verb|\chapter[Poem]{A Japanese Introduction}| command has
  been used with an optional argument to generate a title and to list
  this ``chapter'' in the table of contents as ``Poem''.  If one did
  not desire to have an entry in the table of contents, then one would
  just use the starred command \verb|\chapter*{}|.  The use of an
  optional argument is useful for long chapter and section titles that
  take up too much space in the table of contents.
\end{itemize}

% Parts are the largest units
\part{Thesis}

% Chapters are the next main unit.
\chapter{This is a Chapter}

% Sections are a sub-unit
\section{A Section}
Here is a section with some text.  Equations look like this $y=x$.

@@

% Subsections follow
\subsection{This is a Subsection}
Here is an example of a citation: \cite{Forbes:2006ba}.  The actual
form of the citation is governed by the bibliographystyle.  These
citations are maintained in a BIBTeX file \texttt{sample.bib}.  You
could type these directly into the file.  For an example of the format
to use look at the file \texttt{mitsample.bbl} after you compile this
file.

@@

\subsubsection{This is a Subsubsection}
Here are some more citations \cite{LL3:1977,Peccei:1989,Turner:1999}.
If you use the \texttt{natbib} package with the \verb+sort&compress+
option, then the following citation will look the same as the first
citation in this section: \cite{Turner:1999,Peccei:1989,LL3:1977}.

@@

\paragraph{This is a Paragraph}
Paragraphs and subparagraphs are the smallest units of text.  There is
no subsubsubsection etc.

\subparagraph{This is a Subparagraph}
This is the last level of organisation.  If you need more than this,
you should consider reorganizing your work\dots

\begin{equation}
  \mathrm{f}(x)=\int_{-\infty}^{\int_{-\infty}^x
    e^{-\frac{y^2}{2}}\mathrm{d}{y}}e^{-z^2}\mathrm{d}z
\end{equation}

In order to show you what a separate page would look like (i.e. without
a chapter heading) I must type some more text.  Thus I will babble a
bit and keep babbling for at least one more page\ldots  What you
should notice is that the chapter titles appear substantially lower
than the continuing text. Babble babble
babble babble babble babble babble babble babble babble babble babble
babble babble babble babble babble babble babble babble babble babble
babble babble babble babble babble babble babble babble babble babble
babble babble babble babble babble babble babble babble babble.

@@

\begin{table}[t]                 %optional [t, b or h];
  \begin{tabular}{|r||r@{.}l|}
    \hline
    Phoenix & \$960&35\\
    \hline
    Calgary & \$250&00\\
    \hline
  \end{tabular}
  \caption{
    \label{tab:Table1}
    Here is the caption for this wonderful table.Text of Caption}
\end{table}

\chapter[Another Chapter\ldots]{Another Chapter with a Very Long
  Chapter-name that will Probably Cause Problems}
This chapter name is very long and does not display properly in the
running headers or in the table of contents.  To deal with this, we
provide a shorter version of the title as the optional argument to the
\verb|\chapter[]{}| command.

\section{Another Section}
Another bunch of text to demonstrate what this file does.
You might want a list for example:
\begin{itemize}
\item An item in a list.
\item Another item in a list.
\end{itemize}

\section*{An Unnumbered Section That is Not Included in the Table of
  Contents}
%% We would like to place the figure here, so we start with [h].
%% Note that we have located the figure between paragraphs (rather,
%% before one) so that it does not split up sentences.
\begin{figure}[ht]
  \begin{center}
%% psfrag: comment the following line if not using the psfrag package
    \psfrag{pie makes me happy!}{$\pi$ makes me happy!}
%% includegraphics: comment the following if not using the graphicx package
    \includegraphics[width=0.4\textwidth]{fig.eps}
    \caption[Happy Face: figure example.]{\label{fig:happy} This is a
      figure of a happy face with a \texttt{psfrag} replacement.  The
      original figure (drawn in xfig and exported to a .eps file) has
      the text ``pie makes me happy!''.  The \texttt{psfrag} package
      replaces this with ``$\pi$ makes me happy!''.  Note that we have
      used the optional argument for the caption command so that only
      a short version of this caption occurs in the list of figures.}
  \end{center}
\end{figure}
\afterpage{\clearpage}
Here is an example of a figure environment.
Perhaps I should say that the example of a figure can be seen in
Figure~\ref{fig:happy}.  Figure placement can be tricky with \LaTeX\
because figures and tables are treated as ``floats'': text can flow
around them, but if there is not enough space, they will appear later.
To prevent figures from going too far, the
\verb|\afterpage{\clearpage}| command can be used.  This makes sure
that the figure are typeset at the end of the page (possibly appear on
their own on the following pages) and before any subsequent text.

@@

Be careful when using the ``here'' placement option
\verb|\begin{figure}[ht]| that you place the figure between paragraphs
in your text, otherwise \LaTeX{} might actually insert it in the
middle of a sentence (which does not look very good and is frowned
upon by the editors!)

\subsection*{An Unnumbered Subsection}
Note that if you use subsections or further divisions under an
unnumbered section, then you should make them unnumbered as well
otherwise you will end up with zeros in the section numbering.

\chapter{Landscape Mode}
The landscape mode allows you to rotate a page through 90 degrees.  It
is generally not a good idea to make the chapter heading landscape,
but it can be useful for long tables etc.

\begin{landscape}
  This text should appear rotated, allowing for formatting of very
  wide tables etc.  Note that this might only work after you convert
  the \texttt{dvi} file to a postscript (\texttt{ps}) or \texttt{pdf}
  file using \texttt{dvips} or \texttt{dvipdf} etc.  This feature is
  provided by the \verb|lscape| and the \verb|pdflscape| packages.
  The latter is preferred if it works as it also rotates the pages in
  the pdf file for easier viewing.
\end{landscape}

% This file is setup to use a bibtex file sample.bib and uses the
% plain style.  Note, the bibliography could come after the appendices.
\bibliographystyle{plain}
\bibliography{sample}

% If you only have one appendix, please uncomment the following line.
\appendix
\chapter{First Appendix}
Here you can have your appendices.  Note that if you only have a
single appendix, you should issue
\verb|\renewcommand{\appendicesname}{Appendix}| before calling
\verb|\appendix| to display the singular ``Appendix'' rather than the
default plural ``Appendices''.

\chapter{Second Appendix}
Here is the second appendix.

%% This changes the headings and chapter titles (no numbers for
%% example).
\backmatter
